Oracle Bone Inscription Recognition\\ with CNN and Template Matching

### 2019-12-15 2-oracle/report/paper.tex
make terminology consistent

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Oracle Bone Character Recognition\\ with CNN and Template Matching}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{
	Zhongye~Wang,~\IEEEmembership{SJTU,}
	Jinyu~Li,~\IEEEmembership{SJTU,}
	Xiaoyi~Bao,~\IEEEmembership{SJTU,}
	Shangning~Xu,~\IEEEmembership{SJTU,}
	and Chenxuan~Li,~\IEEEmembership{SJTU}
}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
	In this project, we tackle the task of oracle bone character detection based on the dataset created in class.
	Due to the limit size of dataset, we first augment data with affine transforms and noise transforms to obtain a larger and more robust dataset.
	We then apply a simple CNN and template matching to implement models that can distinguish bone characters between micro categories (40 classes) and macro categories (10 classes).
	We examine models using our homebrew bone character dataset and find the optimal models for micro and macro category classification tasks.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
	Oracle bone character recognition, CNN, template matching, data augmentation.
\end{IEEEkeywords}

@@

\section{Introduction}
\IEEEPARstart{O}{racle} bone inscription (OBI) is the earliest known Chinese writing, which dates back to the late 2nd millennium BC. Detection and recognition of oracle bone inscription is crucial for the understanding of the social and political characteristics of ancient Chinese. It is also significant in education and arts nowadays, as OBI is a cultural heritage of both China and the human civilization.

@@

% wzy
\section{Data Augmentation}
The original dataset contains 40 micro categories of oracle bone characters, each with 85 samples.
Therefore, we have $40 \times 85 = 3400$ samples in total.
This is barely enough for training a convolutional neural network without overfitting, and we need to apply data augmentation to obtain larger dataset adequate for training.

@@

\section{Character Recognition}
We use two different methods to address the character recognition task for oracle bone characters.
We first learn a deep convolutional neural network to recognize characters, then use the template matching method for the same task.

% wzy
\subsection{Convolutional Neural Network}
The deep neural network for learning the oracle bone characters has the structure in Figure~\ref{fig:network}.

@@

% ljy
\subsection{Template Matching}
For the oracle bone character recognition task, we also try a traditional method, template matching, to solve it.

@@

\subsection{Test Set}
We test models on our homebrew dataset where we write oracle bone characters using different pens, on different papers, and captured under different lighting condition.
Figure~\ref{fig:testset} shows samples in the test set.
We can see that the background color and character color varies dramatically from those of the original dataset.
Moreover, there are other noises such as the texture of the paper that could disturb our models.
\begin{figure}[h]
	\centering
	\includegraphics[width=0.19\linewidth]{fig/testset/test_bxy_2_30.jpg}
	\includegraphics[width=0.19\linewidth]{fig/testset/test_lcx_1_40.jpg}
	\includegraphics[width=0.19\linewidth]{fig/testset/test_ljy_2_28.jpg}
	\includegraphics[width=0.19\linewidth]{fig/testset/test_wzy_1_30.jpg}
	\includegraphics[width=0.19\linewidth]{fig/testset/test_xsn_2_28.jpg}
	\caption{Samples in Test Set}
	\label{fig:testset}
\end{figure}

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Oracle Bone Inscription Recognition\\ with CNN and Template Matching}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{
	Zhongye~Wang,~\IEEEmembership{SJTU,}
	Jingyu~Li,~\IEEEmembership{SJTU,}
	Xiaoyi~Bao,~\IEEEmembership{SJTU,}
	Shangning~Xu,~\IEEEmembership{SJTU,}
	and Chenxuan~Li,~\IEEEmembership{SJTU}
}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
	In this project, we tackle the task of oracle bone inscription (OBI) detection based on the dataset created in class.
	Due to the limit size of dataset, we first augment data with affine transforms and noise transforms to obtain a larger and more robust dataset.
	We then apply a simple CNN and template matching to implement models that can distinguish bone characters between micro categories (40 classes) and macro categories (10 classes).
	We examine models using our homebrew bone character dataset and find the optimal models for micro and macro category classification tasks.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
	OBI recognition, CNN, template matching, data augmentation.
\end{IEEEkeywords}

@@

\section{Introduction}
\IEEEPARstart{O}{racle} bone inscription (OBI) is the earliest known Chinese writing, which dates back to the late 2nd millennium BC. Detection and recognition of OBI is crucial for the understanding of the social and political characteristics of ancient Chinese. It is also significant in education and arts nowadays, as OBI is a cultural heritage of both China and the human civilization.

@@

% wzy
\section{Data Augmentation}
The original dataset contains 40 micro categories of OBIs, each with 85 samples.
Therefore, we have $40 \times 85 = 3400$ samples in total.
This is barely enough for training a convolutional neural network without overfitting, and we need to apply data augmentation to obtain larger dataset adequate for training.

@@

\section{Character Recognition}
We use two different methods to address the character recognition task for OBIs.
We first learn a deep convolutional neural network to recognize characters, then use the template matching method for the same task.

% wzy
\subsection{Convolutional Neural Network}
The deep neural network for learning the OBIs has the structure in Figure~\ref{fig:network}.

@@

% ljy
\subsection{Template Matching}
For the OBI recognition task, we also try a traditional method, template matching, to solve it.

@@

\subsection{Test Set}
We test models on our homebrew dataset where we write OBIs using different pens, on different papers, and captured under different lighting condition.
Figure~\ref{fig:testset} shows samples in the test set.
We can see that the background color and character color varies dramatically from those of the original dataset.
Moreover, there are other noises such as the texture of the paper that could disturb our models.
\begin{figure}[h]
	\centering
	\includegraphics[width=0.19\linewidth]{fig/testset/test_bxy_2_30.jpg}
	\includegraphics[width=0.19\linewidth]{fig/testset/test_lcx_1_40.jpg}
	\includegraphics[width=0.19\linewidth]{fig/testset/test_ljy_2_28.jpg}
	\includegraphics[width=0.19\linewidth]{fig/testset/test_wzy_1_30.jpg}
	\includegraphics[width=0.19\linewidth]{fig/testset/test_xsn_2_28.jpg}
	\caption{Samples in Test Set}
	\label{fig:testset}
\end{figure}
